---
title: "Laszlo Szabo's CV"
author:
  firstname: Laszlo
  lastname: Szabo
  address: "Cardiff and Vale University HB, Cardiff, UK"
  position: Consultant Transplant Surgeon
  contacts:
    - icon: fa envelope
      text: Laszlo.Szabo@wales.nhs.uk
      url: "mailto:Laszlo.Szabo@wales.nhs.uk"
    - icon: fa brands orcid
      text: 0000-0002-6881-1542
      url: https://orcid.org/0000-0002-6881-1542
    - icon: fa brands github
      text: Laszlo75
      url: https://github.com/Laszlo75
    - icon: fa brands linkedin
      text: drszabolaszlo
      url: https://linkedin.com/in/drszabolaszlo
style:
   color-accent: "005EB8"
   font-header: "SF Pro Text"
   font-text: "SF Pro Text"
format: awesomecv-typst

execute:
  echo: false
  warning: false
  message: false
---

```{r}
#| label: load-packages
library(typstcv)
```

## Education

```{r}
#| label: education
#| output: asis

education <- read.csv("data/education.csv")

# typstcv needs Date columns for format_date()
education$start <- as.Date(paste0(education$start, "-01-01"))
education$end <- as.Date(paste0(education$end, "-01-01"))

education |>
  format_date(end = "end", date_format = "%Y", sort_by = "end") |>
  resume_entry()
```

## Qualifications

```{r}
#| label: qualifications
#| output: asis

qualifications <- read.csv("data/qualifications.csv")

qualifications |>
  resume_entry(details = "detail")
```

## Certificates

```{r}
#| label: certificates
#| output: asis

certs <- read.csv("data/certificates.csv")
certs <- certs[order(as.numeric(certs$date), decreasing = TRUE), ]

# Write raw Typst inside a passthrough block so Pandoc doesn't touch it.
# Content blocks [] allow #link() to be evaluated (strings "" do not).
lines <- c("```{=typst}")
for (i in seq_len(nrow(certs))) {
  row <- certs[i, ]
  if (!is.na(row$url) && row$url != "") {
    lines <- c(
      lines,
      paste0(
        '#resume-entry(title: "',
        row$title,
        '", date: "',
        row$date,
        '", description: [',
        row$issuer,
        ' #link("',
        row$url,
        '")[\u2197]])'
      )
    )
  } else {
    lines <- c(
      lines,
      paste0(
        '#resume-entry(title: "',
        row$title,
        '", date: "',
        row$date,
        '", description: "',
        row$issuer,
        '")'
      )
    )
  }
}
lines <- c(lines, "```")
cat(paste(lines, collapse = "\n"), "\n")
```

## Work Experience

```{r}
#| label: work-experience
#| output: asis

work <- read.csv("data/work.csv")

# Convert to Date for format_date(); "present" becomes NA (shown as "Present")
work$start <- as.Date(paste0(work$start, "-01-01"))
work$end <- as.Date(ifelse(
  work$end == "present",
  NA,
  paste0(work$end, "-01-01")
))

work |>
  format_date(end = "end", date_format = "%Y", sort_by = "start") |>
  resume_entry()
```

\newpage

## Leadership Roles

```{r}
#| label: roles
#| output: asis

roles <- read.csv("data/roles.csv")

# Rename to match typstcv expected columns
names(roles)[names(roles) == "organisation"] <- "description"

resume_entry(roles)
```

## Research

**Principal Investigator**

```{r}
#| label: research
#| output: asis

research <- read.csv("data/research.csv")

# Rename to match typstcv expected columns (order matters!)
names(research)[names(research) == "title"] <- "description"
names(research)[names(research) == "acronym"] <- "title"

resume_entry(research)
```

## Skills

```{r}
#| label: skills
#| output: asis

skills <- read.csv("data/skills.csv")

# Rename to match typstcv expected columns
names(skills)[names(skills) == "category"] <- "title"

resume_entry(skills)
```

\newpage

```{=typst}
#bibliography("assets/my-publication-list.bib", title: "Publications", full: true, style: "/assets/apa-cv.csl")
```
